The effects of linkage disequilibrium on maintaining balanced polymorphisms in seasonal adaptation

### 2019-12-01 writing/manuscript.Rmd
started writing up results section

require(tidyverse)
require(cowplot)
source(here::here("functions.R"))
```

@@

>>>>

require(tidyverse)
require(cowplot)
require(rlist)
require(png) 
require(knitr)
source(here::here("functions.R"))
```

@@

We first tested whether we were succsessful in reimplementing the model made by @Wittmann2017. We too found that with no linkage (i.e. cross-over happens at every loci) the both proportion of fixed loci (p = 2.52e-07) and standard deviation of loci frequencies (p = 4.63e-07) are lower when dominance is 0.8 compared to when dominance is 0.5.

```{r, message = FALSE, include=FALSE}
setwd(here::here("results/cross_over"))
values = c("d_0.5_y_1_c_0.5", "d_0.8_y_1_c_0.5")
b <- do_analysis(values, "Dominance", "b2") # Dominance is going to be the x axis label, if boxplot number = b3 the third boxplot will be returned
```
```{r, echo = FALSE}
b
```

```{r, fig.width = 2}
# Small fig.width
knitr::include_graphics("D05C05.png")
knitr::include_graphics("D08C05.png")
```
